Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-04-16 paper/ifo-complexAudio.tex
fixing plots - part 1

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/psd_butterworth_14_6.pdf}
	\caption{\label{fig:psd_noise}
\han{If we do not cover the butterworth filter in the main text, I'd suggest only showing the top panel of this figure in the main text. We can include the twp panel version in the butterworth section of the supplementary material}
Top: power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white. 
After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=.49\textwidth]{figures/psd_podo_14_6.pdf}
	\caption{\label{fig:psd_noise}
\han{If we do not cover the butterworth filter in the main text, I'd suggest only showing the top panel of this figure in the main text. We can include the twp panel version in the butterworth section of the supplementary material}
Power spectral density (PSD) of background noise from the optical microphone (with the speaker off). 
% Bottom: the PSD after applying a Butterworth bandpass filter (bottom panel) between the two frequencies marked with red, dashed lines. 
We see strong power from the $50\,{\rm Hz}$ mains hum and its harmonics (most likely from the photodiode circuit and the room’s lighting and cooling). Otherwise, the PSD is fairly white except for a peak at around 0.75~kHz. 
% After filtering we see strong attenuation (at least 3~dB) of all frequencies outside the band, but little change to the harmonics within the band.
}
\end{figure}
